Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-10-21 algorithm.tex
AA: ultimati i TODO AND sul testo

	\begin{enumerate}
	\item \emph{high innovation regions}, whose innovation score exceeds the average score of the previous era by a factor of $\alpha$, i.e.
	\[
	\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
	\]
	 where $\alpha$ is a constant defined by the designer (for example
	$\alpha=1.2$). 	
		\comment{AA: Secondo me e' strano usare $\alpha\cdot is_{av,i-1}$ come soglia. Non si capisce perche' non si usi $is_{av,i}$ ma si usi quello dell'era precedente. Non e' motivata da nessuna parte. Non si capisce perche', in una finale di miss italia, io dovrei conforntare le ragazze di oggi con la ragazza media dell'anno scorso. E' piu' naturale confrontare le ragazze di oggi con la ragazza media di oggi stesso, per vedere chi e' oltre alla media attuale. Che ne dici di cambiare l'espressione in 
			\[
			\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i}\right\} 
			\]
		}
	\item \emph{low innovation regions}, whose score is positive but modest, i.e.
	\[
	\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
	\]
	\item \emph{no innovation regions}, whose innovation is null, i.e. 
	\[
	\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
	\]
	\end{enumerate}

>>>>

	\begin{enumerate}
	\item \emph{high innovation regions}, whose innovation score exceeds the average score of the previous era by a factor of $\alpha$, i.e.
	\[
	\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
	\]
	 where $\alpha$ is a constant defined by the designer (for example
	$\alpha=1.2$). 	
	\item \emph{low innovation regions}, whose score is positive but modest, i.e.
	\[
	\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
	\]
	\item \emph{no innovation regions}, whose innovation is null, i.e. 
	\[
	\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
	\]
	\end{enumerate}

### 2014-10-21 appendix.tex
AA: ultimati i TODO AND sul testo

>>>>

\subsection{Region classification}
Refer to step 7 of the algorithm.
AA: Secondo me e' strano usare $\alpha\cdot is_{av,i-1}$ come soglia. Non si capisce perche' non si usi $is_{av,i}$ ma si usi quello dell'era precedente. Non e' motivata da nessuna parte. Non si capisce perche', in una finale di miss italia, io dovrei conforntare le ragazze di oggi con la ragazza media dell'anno scorso. E' piu' naturale confrontare le ragazze di oggi con la ragazza media di oggi stesso, per vedere chi e' oltre alla media attuale. Che ne dici di cambiare l'espressione in 
			\[
			\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i}\right\} 
			\]
?

### 2014-10-21 concepts.tex
AA: ultimati i TODO AND sul testo

>>>>

In this section and the following one, we will deliberately keep our formulation as general as possible, even if the focus of this paper is the embedded system design space exploration. The goal is to make the generality of PS emerge. We argue that it is a strong point for PS, as for genetic algorithms, since (i) it permits to apply it to a wide range of different problems and (ii) it can be effectually used when the embedded system design is particularly challenging and no much a-priori knowledge is available to the designer. As already pointed in \secL{related_work}, the generality of genetic algorithms has made them widely deployed with respect to the other approaches.
Thanks to the generality of PS, we will not need to modify or adapt it in order to apply it to the case of embedded system design, as we will show in \secL{ee}. On the one hand, this legitimate our choice of keeping formulation general. On the other hand, more importantly, this confirms the capability of PS to automatically adapt to the problem under investigation, without any explicit intervention or knowledge of the designer, required, on the contrary, by~\cite{givargis_tvlsi02,santosh_hptr00,dellnitz2005covering} .
